---
title: "Benchmarking MStargetR against MetaboAnalyst 6.0: feature coverage, runtime, and output equivalence for targeted LC-MS metabolomics"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    df_print: kable
    theme: flatly
params:
  bench_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", out.width = "85%")
library(ggplot2)

# Resolve the benchmark folder (results/ holds the CSVs + PNGs).
bd <- params$bench_dir
if (is.null(bd) || !nzchar(bd)) {
  src <- tryCatch(knitr::current_input(dir = TRUE), error = function(e) NA)
  cfg <- if (!is.na(src)) file.path(dirname(src), "lib", "config.R") else NA
  if (!is.na(cfg) && file.exists(cfg)) { source(cfg); bd <- bench_dir() }
}
res <- function(f) file.path(bd, "results", f)

read_if <- function(f) {                       # NULL if absent / unreadable / empty
  p <- res(f)
  if (!file.exists(p)) return(NULL)
  out <- tryCatch(utils::read.csv(p, check.names = FALSE, stringsAsFactors = FALSE),
                  error = function(e) NULL)
  if (is.null(out) || nrow(out) == 0) return(NULL)
  out
}
img_if <- function(f) { p <- res(f); if (file.exists(p)) knitr::include_graphics(p) }

# ---- load all result artifacts once ----
hh <- read_if("bm_headtohead.csv")
eq <- read_if("bm_equivalence.csv")
sc <- read_if("bm_scaling.csv")
bm <- if (file.exists(file.path(bd, "bm_res.csv")))
  tryCatch(utils::read.csv(file.path(bd, "bm_res.csv")), error = function(e) NULL) else NULL

# ---- safe numeric accessors for inline prose ----
fmt <- function(x, d = 2) if (length(x) == 0 || !is.finite(x)) "—" else formatC(x, format = "f", digits = d)
# wall-clock for a given engine+stage from the head-to-head table
hh_val <- function(engine, stage, col = "wall_s_median") {
  if (is.null(hh)) return(NA_real_)
  r <- hh[hh$engine == engine & hh$stage == stage, ]
  if (nrow(r) == 0) return(NA_real_)
  suppressWarnings(as.numeric(r[[col]][1]))
}
speedup <- function(stage) {
  ma <- hh_val("MetaboAnalyst", stage); ms <- hh_val("MStargetR", stage)
  if (!is.finite(ma) || !is.finite(ms) || ms == 0) return(NA_real_)
  ma / ms
}
# equivalence metric lookup by comparison label + column
eq_val <- function(comparison, col) {
  if (is.null(eq) || !"comparison" %in% names(eq) || !col %in% names(eq)) return(NA_real_)
  r <- eq[eq$comparison == comparison, ]
  if (nrow(r) == 0) return(NA_real_)
  suppressWarnings(as.numeric(r[[col]][1]))
}
# dataset dimensions from the hash provenance file
dims_txt <- {
  p <- res("shared_table_hash.txt")
  if (file.exists(p)) paste(grep("dims:", readLines(p), value = TRUE), collapse = "") else ""
}
have <- function(x) !is.null(x)
```

```{r abstract_values}
combat_speed <- speedup("combat"); qcrlsc_speed <- speedup("qcrlsc"); pca_speed <- speedup("pca")
combat_ccc <- eq_val("ComBat_corrected_matrix", "ccc_log10")
combat_r   <- eq_val("ComBat_corrected_matrix", "median_r_pearson")
qcrlsc_ccc <- eq_val("QCRLSC_corrected_matrix", "ccc_log10")
pca_rv     <- eq_val("PCA_scores", "rv_coefficient")
```

# Abstract

**Background.** MetaboAnalyst is the de-facto standard platform for metabolomics
data analysis, but it is a generalist tool that begins at the peak-table stage.
MStargetR is a specialised, containerised pipeline for targeted multiple-reaction-
monitoring (MRM) LC-MS lipidomics that spans the full workflow from vendor files
to QC-corrected concentrations. This report quantifies how the two compare on
(i) feature coverage, (ii) runtime and memory, and (iii) numerical equivalence of
their shared analytical steps.

**Methods.** A single peak-intensity table was produced by MStargetR from two real
SCIEX `.wiff` plasma-lipid acquisitions (`r if (nzchar(dims_txt)) sub("dims:", "", dims_txt) else "see Methods"`)
and fed *identically* to both engines. MetaboAnalyst was run via its R engine
(`MetaboAnalystR`, GitHub HEAD, package 4.3.0) inside a pinned Docker image.
Both engines were pinned to a single compute thread. We compared the two batch-
correction methods both implement (**ComBat**, **QC-RLSC**) and **PCA**, timing each
with warm-median wall-clock and peak RAM, and assessed output equivalence with
per-feature correlation, Lin's concordance correlation coefficient (CCC), RMSE on
the log10 scale, QC-RSD concordance, and the rotation-invariant RV coefficient /
Procrustes test for PCA scores.

**Results.** On identical input, the two engines produce **numerically equivalent**
corrected matrices — ComBat CCC = `r fmt(combat_ccc, 3)` (median per-feature
Pearson r = `r fmt(combat_r, 3)`), QC-RLSC CCC = `r fmt(qcrlsc_ccc, 3)` — and
near-congruent PCA geometry (RV = `r fmt(pca_rv, 3)`). MStargetR was
**`r fmt(combat_speed, 1)`×** faster than MetaboAnalyst on ComBat and comparable on
QC-RLSC, at similar memory. MStargetR additionally covers vendor-file conversion,
Skyline peak picking, QC-random-forest correction, and per-plate QC reporting that
MetaboAnalyst does not; MetaboAnalyst covers pathway/enrichment, biomarker ROC,
untargeted processing, and a broader multivariate/correction suite.

**Conclusion.** For the steps both tools share, MStargetR reproduces MetaboAnalyst's
results while delivering the targeted-lipidomics front end and QC machinery
MetaboAnalyst lacks; the two are complementary rather than competing.

# Introduction

MetaboAnalyst (currently version 6.0) is the most widely used platform for
downstream metabolomics statistics and functional interpretation. It assumes the
user already has a feature/peak table and excels at normalisation, multivariate
statistics, enrichment and pathway analysis. **MStargetR** addresses a different
part of the workflow: it is a reproducible, container-driven pipeline purpose-built
for *targeted* MRM LC-MS lipidomics, taking raw vendor files through ProteoWizard
conversion, Skyline peak integration, QC assessment, batch/drift correction and
reporting.

Because the two tools overlap on a well-defined subset of steps — missing-value
handling, RSD/percent filtering, normalisation, **ComBat** and **QC-RLSC** batch
correction, and **PCA** — a fair, quantitative comparison is possible on that
subset, while the non-overlapping capabilities are documented qualitatively. The
goals of this benchmark are to (1) map feature coverage, (2) measure runtime and
memory on identical data, and (3) verify that, where the tools claim to do the same
thing, they produce the same numbers.

> **Version note.** "MetaboAnalyst 6.0" is the web service; the analytical engine is
> the R package `MetaboAnalystR`. The pinned Docker image installs it from the
> xia-lab GitHub HEAD (package version 4.3.0 at build time). All MetaboAnalyst
> numbers here are from that R engine, single-threaded, in the pinned image — the
> hosted web UI is explicitly out of scope (its timings are not reproducible).

# Methods

## Data

A single shared peak-intensity table was generated by MStargetR (msConvertR →
PeakForgeR) from two real SCIEX `.wiff` plasma-lipid acquisitions and then supplied
**byte-for-byte identically** to both engines (verified by SHA-256 hash). Using one
shared table is essential: it removes peak-picking as a confound so the comparison
isolates the shared downstream steps.

```{r provenance}
p <- res("shared_table_hash.txt")
if (file.exists(p)) cat(readLines(p), sep = "\n") else cat("shared_table_hash.txt not found.")
```

## Environment and fairness controls

```{r env}
cat("R (host):", R.version.string, "\n")
cat("MetaboAnalyst engine: MetaboAnalystR 4.3.0 (xia-lab GitHub HEAD) in Docker image mstargetr-bench/metaboanalystr.\n")
cat("\nFairness controls:\n")
cat(" - Single-thread pinned on both engines (OMP/OpenBLAS/MKL/data.table = 1).\n")
cat(" - MetaboAnalyst container limited to --cpus=1 --memory=8g.\n")
cat(" - One untimed warm-up per stage; warm-median reported.\n")
cat(" - Container start-up excluded (timer is inside the in-container runner).\n")
cat(" - Identical, hash-verified input table for both engines.\n")
```

MStargetR runs natively on the Windows host; MetaboAnalyst runs in the Docker
container. Both are pinned to a single thread so the comparison reflects single-core
compute. Timing uses a warm-up iteration followed by repeated timed runs
(`peakRAM` for resident peak memory; in-container compute time for the MetaboAnalyst
side, which excludes container start-up).

## Comparable stages and statistics

The two batch-correction methods both engines implement — **ComBat** (both wrap
`sva::ComBat`) and **QC-RLSC** (both implement the Dunn et al. LOESS approach) — plus
**PCA**, form the quantitative head-to-head. Output equivalence is assessed after
re-keying both outputs by `(sample, feature)` and intersecting, using: per-feature
Pearson/Spearman correlation; Lin's concordance correlation coefficient (CCC);
RMSE/MAE on the log10 scale; QC-RSD concordance; and, for PCA, the rotation/sign/
scale-invariant RV coefficient with a Procrustes (PROTEST) permutation test.

# Results

## Feature parity matrix

```{r parity}
parity <- read.csv(text = "Capability|MStargetR|MetaboAnalyst 6.0|Notes
Vendor file to mzML|Yes (msConvertR / ProteoWizard)|No|MStargetR-unique
Targeted peak picking (Skyline)|Yes (PeakForgeR)|No|MStargetR-unique
Untargeted / DDA spectral processing|No|Yes (OptiLCMS)|MA-unique
Data upload + sanity check|Yes|Yes (Read.TextData / SanityCheckData)|Comparable
MV imputation min/half|Yes (minHalf)|Yes (ImputeMissingVar lod)|Direct map
MV imputation mean/median/KNN|Yes|Yes (knn_smp / knn_var)|MA offers more variants
MV imputation BPCA/PPCA/SVD|No|Yes|MA-richer
Filter by % missing|Yes|Yes (RemoveMissingByPercent)|Comparable
Filter by QC %RSD|Yes (coCV)|Yes (FilterVariable rsd)|Direct map
Filter by IQR/MAD/SD/mean|No|Yes|MA-richer
SIL internal-standard filtering|Yes|No|MStargetR-unique
Normalization / transform / scale|log / pareto / auto|Yes (Normalization)|MA broader sample norm
Batch correction: ComBat|Yes (sva)|Yes (PerformBatchCorrection Combat)|Head-to-head
Batch correction: QC-RLSC|Yes (qcrlscR)|Yes (QC_RLSC)|Head-to-head
Batch correction: QCRFSC (random forest)|Yes (statTarget)|No|MStargetR-unique
Batch correction: WaveICA/EigenMS/RUV/NOMIS/CCMN|No|Yes|MA-richer
PCA|Yes (ropls / prcomp)|Yes (PCA.Anal)|Head-to-head (scaling aligned)
PLS-DA / OPLS-DA|OPLS via ropls|Yes (full suite)|MA-richer supervised
Pathway / enrichment|No|Yes|MA-unique
Biomarker / ROC|No|Yes|MA-unique
QC RSD reporting (LTR/PQC, per-plate)|Yes (rich)|Partial|MStargetR-richer
Multi-plate / multi-method|Yes|Limited|MStargetR-unique
Interactive HTML + Excel reports|Yes|Yes (web)|Both
Programmatic R API|Yes|Yes (MetaboAnalystR)|Both", sep = "|", check.names = FALSE)
knitr::kable(parity)
```

The overlap is the data-conditioning core (imputation, filtering, normalisation,
ComBat/QC-RLSC, PCA). MStargetR is *deeper* on the targeted-lipidomics front end and
QC; MetaboAnalyst is *broader* downstream (supervised multivariate, enrichment, ROC,
untargeted). The tools are largely complementary.

## Runtime head-to-head

```{r timing}
if (have(hh)) {
  show <- hh[order(hh$stage, hh$engine),
             intersect(c("engine","stage","wall_s_median","wall_s_sd","peak_mb"), names(hh))]
  knitr::kable(show, digits = 3,
               caption = "Warm-median wall-clock (s) and peak RAM (MiB) by stage and engine.")
} else cat("_bm_headtohead.csv not yet available._")
```

```{r timing_plot, fig.cap="Wall-clock (warm median, log scale) for the shared stages."}
if (have(hh)) {
  shared <- hh[hh$stage %in% c("combat","qcrlsc","pca") & is.finite(hh$wall_s_median), ]
  if (nrow(shared) > 0) {
    ggplot(shared, aes(stage, wall_s_median, fill = engine)) +
      geom_col(position = position_dodge(0.8), width = 0.7) +
      scale_y_log10() +
      labs(x = NULL, y = "wall-clock (s, warm median, log scale)", fill = NULL,
           title = "Shared-stage runtime") +
      theme_bw(base_size = 12)
  }
}
```

```{r timing_prose, results="asis"}
if (have(hh)) {
  cat(sprintf(paste0(
    "On the shared batch-correction stages, MStargetR completed **ComBat in %s s** ",
    "versus **%s s** for MetaboAnalyst (**%s× faster**), and **QC-RLSC in %s s** ",
    "versus **%s s** (%s× — comparable, both LOESS-bound). PCA was %s s vs %s s. ",
    "The ComBat gap reflects MStargetR calling `sva::ComBat` directly with minimal ",
    "wrapping, whereas the MetaboAnalyst path carries additional object-management ",
    "and I/O overhead.\n\n"),
    fmt(hh_val("MStargetR","combat")), fmt(hh_val("MetaboAnalyst","combat")), fmt(speedup("combat"),1),
    fmt(hh_val("MStargetR","qcrlsc")), fmt(hh_val("MetaboAnalyst","qcrlsc")), fmt(speedup("qcrlsc"),1),
    fmt(hh_val("MStargetR","pca")), fmt(hh_val("MetaboAnalyst","pca"))))
}
```

## Complete-pipeline comparison

The per-stage rows above are useful for locating where time is spent, but
**summing them overstates total cost on the MetaboAnalyst side**: each stage in
that breakdown runs in its own Docker container (≈ one R-session bootstrap +
MetaboAnalystR load per stage). The rows below time the realistic end-to-end
batch-correction + ordination pipeline in **one process per engine**: a single
`MStargetR::batchCorrectR` call (which folds in MA's separately-billed
impute / filter / normalize / correct steps) plus an autoscaled `prcomp`,
versus a single MA container invocation chaining
`Read.BatchDataTB → PerformBatchCorrection → prcomp`.

```{r fullpipe_table}
fp_stages <- c("full_combat", "full_qcrlsc")
if (have(hh) && any(hh$stage %in% fp_stages)) {
  fp <- hh[hh$stage %in% fp_stages, , drop = FALSE]
  fp <- fp[order(fp$stage, fp$engine),
           intersect(c("engine","stage","wall_s_median","wall_s_sd","peak_mb",
                       "host_total_s"), names(fp))]
  knitr::kable(fp, digits = 3,
               caption = paste0("End-to-end pipeline wall-clock (s) and peak RAM (MiB).",
                                " host_total_s, where present, is the host-side wall-clock",
                                " including container start-up (MetaboAnalyst only)."))
} else cat("_Complete-pipeline rows not present; re-run `Rscript benchmark/02_headtohead.R`._")
```

```{r fullpipe_prose, results="asis"}
if (have(hh) && any(hh$stage %in% fp_stages)) {
  fc_ms <- hh_val("MStargetR","full_combat");   fc_ma <- hh_val("MetaboAnalyst","full_combat")
  fq_ms <- hh_val("MStargetR","full_qcrlsc");   fq_ma <- hh_val("MetaboAnalyst","full_qcrlsc")
  fc_speed <- if (is.finite(fc_ms) && is.finite(fc_ma) && fc_ms > 0) fc_ma / fc_ms else NA_real_
  fq_speed <- if (is.finite(fq_ms) && is.finite(fq_ma) && fq_ms > 0) fq_ma / fq_ms else NA_real_
  cat(sprintf(paste0(
    "Running the full **ComBat** pipeline (batch correction + autoscaled PCA) ",
    "in one process took **%s s** on MStargetR versus **%s s** on MetaboAnalyst ",
    "(%s× faster). The full **QC-RLSC** pipeline took **%s s** vs **%s s** ",
    "(%s×). These figures are the apples-to-apples \"how long does an analysis ",
    "take\" numbers; the per-stage table above remains useful for diagnosing ",
    "where the time goes within each engine.\n\n"),
    fmt(fc_ms), fmt(fc_ma), fmt(fc_speed,1),
    fmt(fq_ms), fmt(fq_ma), fmt(fq_speed,1)))
}
```

## Scaling behaviour

Both engines were timed on the same bootstrapped tables across a grid of sample,
feature, and batch counts.

```{r scaling_plots}
img_if("bm_scaling_samples.png")
img_if("bm_scaling_features.png")
img_if("bm_scaling_batches.png")
img_if("bm_memory.png")
```

```{r scaling_exponents}
if (have(sc) && "axis" %in% names(sc)) {
  ss <- sc[sc$axis == "samples" & is.finite(sc$wall_s_median) & sc$wall_s_median > 0, ]
  if (nrow(ss) > 0) {
    ss$grp <- paste(ss$engine, ss$method)
    exps <- do.call(rbind, lapply(split(ss, ss$grp), function(d) {
      if (length(unique(d$n_samples)) < 2) return(NULL)
      b <- coef(lm(log10(wall_s_median) ~ log10(n_samples), d))[2]
      data.frame(`engine × method` = d$grp[1], `scaling exponent (samples)` = round(b, 2),
                 check.names = FALSE)
    }))
    if (!is.null(exps)) knitr::kable(exps, row.names = FALSE,
      caption = "Empirical scaling exponent = slope of log10(wall-clock) vs log10(n samples). ~1 is linear.")
  }
} else cat("_bm_scaling.csv not yet available._")
```

## Full-pipeline scaling (MStargetR only)

The vendor → peak-table front end (msConvertR → PeakForgeR → qcCheckR) has **no
MetaboAnalyst counterpart**: MetaboAnalyst cannot ingest `.wiff` files. This section
characterises MStargetR's end-to-end throughput on replicated real acquisitions.

```{r fullpipe}
img_if("../bm_loess.png"); img_if("../bm_linear.png")
if (!is.null(bm)) knitr::kable(bm, caption = "Total pipeline wall-clock vs sample count (MStargetR end-to-end).")
st <- read_if("bm_fullpipe_stages.csv")
if (!is.null(st)) knitr::kable(st, digits = 2,
  caption = "Per-stage breakdown: msConvertR / PeakForgeR / qcCheckR.")
if (is.null(bm)) cat("_bm_res.csv not yet available._")
```

## Output equivalence

The decisive question: on identical input, do the engines agree numerically?

```{r equivalence_table}
if (have(eq) && ncol(eq) > 1) {
  knitr::kable(eq, digits = 3, caption = "Numerical agreement on the shared stages.")
} else cat("_bm_equivalence.csv not yet available._")
```

```{r equivalence_prose, results="asis"}
if (have(eq)) {
  cat(sprintf(paste0(
    "**ComBat** corrected matrices are essentially identical between engines: CCC = ",
    "%s on the log10 scale, median per-feature Pearson r = %s, with %s%% of features ",
    "exceeding r = 0.95. **QC-RLSC** agreement is also strong (CCC = %s, median r = %s). ",
    "Per-feature QC-RSD — the metric analysts actually act on — is concordant (ComBat ",
    "CCC = %s). For unsupervised structure, **PCA** scores are near-congruent: ",
    "RV coefficient = %s (Procrustes PROTEST p = %s). ",
    "Residual ComBat differences are dominated by MStargetR's optional re-centring of ",
    "corrected values to the original QC mean, a deliberate design choice; offset-",
    "invariant metrics (Spearman, RV) are therefore reported alongside RMSE.\n\n"),
    fmt(eq_val("ComBat_corrected_matrix","ccc_log10"),3),
    fmt(eq_val("ComBat_corrected_matrix","median_r_pearson"),3),
    fmt(100*eq_val("ComBat_corrected_matrix","frac_features_r_gt_095"),1),
    fmt(eq_val("QCRLSC_corrected_matrix","ccc_log10"),3),
    fmt(eq_val("QCRLSC_corrected_matrix","median_r_pearson"),3),
    fmt(eq_val("ComBat_rsd","ccc"),3),
    fmt(eq_val("PCA_scores","rv_coefficient"),3),
    fmt(eq_val("PCA_scores","protest_p"),3)))
}
```

```{r equivalence_plots}
ep_dir <- res("equivalence_plots")
eq_pngs <- if (dir.exists(ep_dir)) list.files(ep_dir, pattern = "\\.png$", full.names = TRUE) else character(0)
for (f in eq_pngs) knitr::include_graphics(f)
```

**Alignment notes.** Outputs are re-keyed by `(sample, feature)` and intersected
before comparison (MetaboAnalyst reorders/renames features and appends `.mzML` to
sample names). MStargetR re-centres corrected values to the original QC mean and
reverts coCV-failed features to uncorrected (tagged), whereas MetaboAnalyst drops
them; such features are excluded from agreement metrics. Correlations/CCC are on the
log10 scale; QC-RLSC "subtract" can yield negatives (positive-clamped before
logging). PCA uses autoscaling on both sides with rotation/sign-invariant metrics.

# Discussion

Where MStargetR and MetaboAnalyst implement the same method, they produce the same
numbers: ComBat and QC-RLSC corrected matrices, the per-feature QC-RSD that drives
analyst decisions, and PCA geometry all agree to within the differences explained by
documented design choices (notably MStargetR's QC-mean re-centring). This is the key
validation result — it gives users confidence that MStargetR's correction is a
faithful implementation, not a divergent reinterpretation.

On runtime, MStargetR's direct, low-overhead call into `sva::ComBat` makes it
markedly faster on ComBat at equivalent output; QC-RLSC, dominated by LOESS fitting,
is comparable in both. The practically important difference, however, is *scope*
rather than speed: MStargetR delivers the vendor-to-concentration front end (file
conversion, Skyline peak picking), SIL internal-standard handling, QC-random-forest
correction, and rich per-plate LTR/PQC QC reporting — none of which MetaboAnalyst
provides — while MetaboAnalyst remains the stronger choice for supervised
multivariate analysis, biomarker/ROC, enrichment and pathway interpretation, and
untargeted data. The tools occupy complementary positions in a metabolomics
workflow: MStargetR to produce a clean, QC-corrected targeted table, MetaboAnalyst
to interrogate it downstream.

# Limitations

- **Engine vs web UI.** `MetaboAnalystR` (4.3.0, GitHub HEAD) is the engine behind
  the 6.0 web service; web-only features and the hosted UI's timings are out of scope.
- **Container vs host.** MetaboAnalyst runs single-CPU in Docker, MStargetR on the
  host; both are thread-pinned and container start-up is excluded, but a residual
  containerisation overhead on the MetaboAnalyst side cannot be fully eliminated.
- **PCA implementation.** MetaboAnalyst's `PCA.Anal` depends on packages
  (`RSclient`/`factoextra`) not needed for the scores; the in-container runner
  computes scores with `prcomp` directly (identical to `PCA.Anal`'s core) so PCA
  scores are comparable, but MetaboAnalyst's loadings/contribution plots are not
  reproduced here.
- **Single dataset.** Equivalence and timing are from one real two-plate lipidomics
  cohort; scaling sweeps use bootstrapped resamples of it. Generality across assays
  and instruments is not established.
- **Parameter alignment.** ComBat (`par.prior=TRUE, mean.only=FALSE`) and QC-RLSC
  (LOESS span optimisation) were aligned where the parameters are exposed; residual
  algorithmic defaults may differ.

# Conclusion

On the analytical steps the two tools share, MStargetR reproduces MetaboAnalyst's
output to high numerical fidelity while matching or exceeding its speed. Beyond that
overlap, MStargetR supplies the targeted-lipidomics front end and QC machinery that
MetaboAnalyst lacks, and MetaboAnalyst supplies the downstream statistical and
functional analysis that MStargetR does not target. The two are complementary, and
this benchmark provides a reproducible, hash-verified basis for that claim.

# Reproducibility appendix

All artifacts live in the benchmark results folder. Scripts: `benchmark/01`–`04`
(generation, head-to-head, scaling, equivalence) and this report (`benchmark/05`);
the MetaboAnalyst stage runner is `benchmark/docker/ma_runner.R`; the pinned image is
built from `benchmark/docker/Dockerfile`. See `benchmark/README.md` for the run
order. Inputs are SHA-256 hashed and the hash is recorded with every result.

```{r sessioninfo}
cat("Generated:", format(Sys.time()), "\n")
```
