---
title: "batchCorrectR Batch Correction Report"
author: "MStargetR"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    code_folding: hide
params:
  result: NULL
  original_data: NULL
  qc_label: "qc"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 10, fig.height = 5
)
library(ggplot2)
library(plotly)

result <- params$result
original_data <- params$original_data
qc_label <- tolower(params$qc_label)
cs <- result$correction_summary
met_cols <- cs$metabolite
corrected_data <- result$corrected_data
```

# Overview {.tabset}

## Summary

```{r summary-boxes}
n_mets <- length(met_cols)
n_improved <- sum(cs$improved, na.rm = TRUE)
n_worsened <- sum(!cs$improved & !is.na(cs$improved))
med_before <- round(median(cs$rsd_before, na.rm = TRUE), 1)
med_after <- round(median(cs$rsd_after, na.rm = TRUE), 1)
n_failed_qc <- length(result$failed_qc)
n_batches <- if (!is.null(original_data) && "batch" %in% names(original_data)) {
  length(unique(original_data$batch))
} else { NA }
n_samples <- if (!is.null(original_data)) nrow(original_data) else nrow(corrected_data)
method <- if (!is.null(result$report)) result$report$parameters$method else "Unknown"
```

| Parameter | Value |
|:----------|:------|
| **Method** | `r method` |
| **Samples** | `r n_samples` |
| **Batches** | `r n_batches` |
| **Metabolites** | `r n_mets` |
| **Failed QC injections** | `r n_failed_qc` |
| **Median QC %RSD (before)** | `r med_before`% |
| **Median QC %RSD (after)** | `r med_after`% |
| **Metabolites improved** | `r n_improved` / `r n_mets` (`r round(100 * n_improved / n_mets, 1)`%) |
| **Metabolites worsened** | `r n_worsened` / `r n_mets` |

## Failed QC Injections

```{r failed-qc}
if (length(result$failed_qc) > 0) {
  knitr::kable(data.frame(Sample = result$failed_qc), caption = "Flagged QC injections (signal < 10% batch median)")
} else {
  cat("No QC injections were flagged.")
}
```

# Quality Dashboard {.tabset}

## RSD Distribution

```{r rsd-histogram, fig.height=4}
rsd_df <- data.frame(
  rsd_before = cs$rsd_before,
  rsd_after = cs$rsd_after
)

p <- ggplot() +
  geom_histogram(data = rsd_df, aes(x = rsd_before, fill = "Before"),
                 alpha = 0.5, bins = 30, colour = "white") +
  geom_histogram(data = rsd_df, aes(x = rsd_after, fill = "After"),
                 alpha = 0.5, bins = 30, colour = "white") +
  geom_vline(xintercept = 30, linetype = "dashed", colour = "red", linewidth = 0.5) +
  scale_fill_manual(values = c("Before" = "#E41A1C", "After" = "#377EB8"), name = "Stage") +
  labs(title = "QC %RSD Distribution", x = "%RSD", y = "Count") +
  theme_bw()
ggplotly(p)
```

## Pass / Fail

```{r pass-fail-donut, fig.height=4}
pass_after <- sum(cs$rsd_after <= 30, na.rm = TRUE)
fail_after <- sum(cs$rsd_after > 30, na.rm = TRUE)

plotly::plot_ly(
  labels = c("Pass (RSD <= 30%)", "Fail (RSD > 30%)"),
  values = c(pass_after, fail_after),
  type = "pie", hole = 0.5,
  marker = list(colors = c("#22c55e", "#ef4444")),
  textinfo = "label+percent"
) |> plotly::layout(title = "Metabolite Pass/Fail (After Correction)",
                    showlegend = FALSE)
```

# RSD Comparison {.tabset}

## Before vs After

```{r rsd-comparison, fig.height=6}
rsd_long <- tidyr::pivot_longer(
  data.frame(metabolite = cs$metabolite, Before = cs$rsd_before, After = cs$rsd_after),
  cols = c("Before", "After"), names_to = "stage", values_to = "rsd"
)
rsd_long$stage <- factor(rsd_long$stage, levels = c("Before", "After"))

p <- ggplot(rsd_long, aes(x = reorder(metabolite, rsd), y = rsd, fill = stage)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  geom_hline(yintercept = 30, linetype = "dashed", colour = "red") +
  scale_fill_manual(values = c("Before" = "#E41A1C", "After" = "#377EB8"), name = "Stage") +
  labs(title = "QC %RSD Before vs After Correction", x = "Metabolite", y = "%RSD") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7))
ggplotly(p)
```

## Scatter (Before vs After)

```{r rsd-scatter, fig.height=5}
scatter_df <- data.frame(
  metabolite = cs$metabolite,
  before = cs$rsd_before,
  after = cs$rsd_after,
  improved = cs$improved
)

p <- ggplot(scatter_df, aes(x = before, y = after, colour = improved, text = metabolite)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "grey50") +
  geom_hline(yintercept = 30, linetype = "dotted", colour = "red", linewidth = 0.4) +
  geom_vline(xintercept = 30, linetype = "dotted", colour = "red", linewidth = 0.4) +
  scale_colour_manual(values = c("TRUE" = "#22c55e", "FALSE" = "#ef4444"),
                      labels = c("TRUE" = "Improved", "FALSE" = "Worsened"),
                      name = "Status") +
  labs(title = "RSD: Before vs After", x = "%RSD Before", y = "%RSD After") +
  theme_bw()
ggplotly(p, tooltip = c("text", "x", "y"))
```

# PCA {.tabset}

```{r pca-helper}
run_pca <- function(data, met_cols) {
  mat <- as.matrix(data[, intersect(met_cols, names(data)), drop = FALSE])
  for (j in seq_len(ncol(mat))) {
    nas <- is.na(mat[, j])
    if (any(nas)) mat[nas, j] <- median(mat[, j], na.rm = TRUE)
  }
  col_vars <- apply(mat, 2, var, na.rm = TRUE)
  mat <- mat[, !is.na(col_vars) & col_vars > 0, drop = FALSE]
  if (ncol(mat) < 2) return(NULL)
  pca <- prcomp(mat, center = TRUE, scale. = TRUE)
  var_expl <- round(100 * pca$sdev^2 / sum(pca$sdev^2), 1)
  list(
    df = data.frame(
      PC1 = pca$x[, 1], PC2 = pca$x[, 2],
      sample_type = as.character(data$sample_type),
      batch = as.character(data$batch),
      sample_name = if ("sample_name" %in% names(data)) data$sample_name else seq_len(nrow(data)),
      stringsAsFactors = FALSE
    ),
    var_expl = var_expl
  )
}
```

## Before Correction

```{r pca-before, fig.height=5}
if (!is.null(original_data)) {
  pca_res <- run_pca(original_data, met_cols)
  if (!is.null(pca_res)) {
    p <- ggplot(pca_res$df, aes(x = PC1, y = PC2, colour = sample_type, shape = batch, text = sample_name)) +
      geom_point(size = 2, alpha = 0.7) +
      labs(title = "PCA: Before Correction",
           x = paste0("PC1 (", pca_res$var_expl[1], "%)"),
           y = paste0("PC2 (", pca_res$var_expl[2], "%)"),
           colour = "Sample Type", shape = "Batch") +
      theme_bw()
    ggplotly(p, tooltip = c("text", "x", "y"))
  } else {
    cat("Insufficient data for PCA.")
  }
} else {
  cat("Original data not available. Pass `original_data` to bc_export_html_report().")
}
```

## After Correction

```{r pca-after, fig.height=5}
pca_res <- run_pca(corrected_data, met_cols)
if (!is.null(pca_res)) {
  p <- ggplot(pca_res$df, aes(x = PC1, y = PC2, colour = sample_type, shape = batch, text = sample_name)) +
    geom_point(size = 2, alpha = 0.7) +
    labs(title = "PCA: After Correction",
         x = paste0("PC1 (", pca_res$var_expl[1], "%)"),
         y = paste0("PC2 (", pca_res$var_expl[2], "%)"),
         colour = "Sample Type", shape = "Batch") +
    theme_bw()
  ggplotly(p, tooltip = c("text", "x", "y"))
} else {
  cat("Insufficient data for PCA.")
}
```

# Run Order Plots {.tabset}

```{r run-order-setup}
# Pick top 6 metabolites by pre-correction RSD
n_plot <- min(6, length(met_cols))
top_mets <- names(sort(result$qc_rsd_before, decreasing = TRUE))[seq_len(n_plot)]
```

## Signal Drift

```{r run-order-plots, fig.height=8, results='asis'}
if (!is.null(original_data) && "run_order" %in% names(original_data)) {
  ro_data <- dplyr::bind_rows(
    original_data |>
      dplyr::select(dplyr::any_of(c("sample_name", "batch", "sample_type", "run_order")),
                    dplyr::all_of(top_mets)) |>
      tidyr::pivot_longer(dplyr::all_of(top_mets), names_to = "metabolite", values_to = "value") |>
      dplyr::mutate(stage = "Before"),
    corrected_data |>
      dplyr::select(dplyr::any_of(c("sample_name", "batch", "sample_type", "run_order")),
                    dplyr::all_of(top_mets)) |>
      tidyr::pivot_longer(dplyr::all_of(top_mets), names_to = "metabolite", values_to = "value") |>
      dplyr::mutate(stage = "After")
  ) |>
    dplyr::mutate(
      stage = factor(stage, levels = c("Before", "After")),
      is_qc = tolower(sample_type) == qc_label
    )

  p <- ggplot(ro_data, aes(x = run_order, y = value, colour = is_qc)) +
    geom_point(size = 1.2, alpha = 0.7) +
    facet_wrap(~ metabolite + stage, scales = "free_y", ncol = 2) +
    scale_color_manual(values = c("TRUE" = "#E41A1C", "FALSE" = "#377EB8"),
                       labels = c("TRUE" = "QC", "FALSE" = "Sample"), name = "Type") +
    labs(title = "Run Order: Before vs After Correction",
         x = "Run Order", y = "Signal Intensity") +
    theme_bw() +
    theme(strip.text = element_text(size = 8))
  print(ggplotly(p))
} else {
  cat("Run order data not available in original data.")
}
```

# Correction Summary {.tabset}

## Top Improved

```{r top-improved}
top_imp <- cs |>
  dplyr::filter(improved) |>
  dplyr::arrange(rsd_change) |>
  utils::head(15) |>
  dplyr::select(metabolite, rsd_before, rsd_after, rsd_change, improved)

knitr::kable(top_imp, digits = 2, caption = "Top 15 most improved metabolites (by RSD reduction)")
```

## Worst Affected

```{r worst-affected}
worst <- cs |>
  dplyr::filter(!improved) |>
  dplyr::arrange(dplyr::desc(rsd_change)) |>
  utils::head(15) |>
  dplyr::select(metabolite, rsd_before, rsd_after, rsd_change, improved)

if (nrow(worst) > 0) {
  knitr::kable(worst, digits = 2, caption = "Top 15 worst affected metabolites (RSD increased)")
} else {
  cat("All metabolites showed improvement or no change.")
}
```

## Full Table

```{r full-table}
DT::datatable(
  cs |> dplyr::select(metabolite, rsd_before, rsd_after, rsd_change, improved),
  filter = "top",
  options = list(pageLength = 25, scrollX = TRUE),
  caption = "Full correction summary"
)
```

# Heatmap

```{r heatmap, fig.height=8, fig.width=10}
# Use corrected data, top 30 metabolites by variance
hm_mets <- intersect(met_cols, names(corrected_data))
if (length(hm_mets) > 0) {
  mat <- as.matrix(corrected_data[, hm_mets, drop = FALSE])
  col_vars <- apply(mat, 2, var, na.rm = TRUE)
  top_n <- min(30, length(hm_mets))
  hm_mets <- names(sort(col_vars, decreasing = TRUE))[seq_len(top_n)]
  mat <- mat[, hm_mets, drop = FALSE]

  # Scale for heatmap
  mat_scaled <- scale(mat)
  mat_scaled[is.na(mat_scaled)] <- 0

  row_labels <- if ("sample_name" %in% names(corrected_data)) {
    corrected_data$sample_name
  } else {
    seq_len(nrow(corrected_data))
  }

  plotly::plot_ly(
    x = hm_mets, y = row_labels, z = mat_scaled,
    type = "heatmap",
    colorscale = list(c(0, "#313695"), c(0.5, "#ffffbf"), c(1, "#a50026")),
    hovertemplate = "Metabolite: %{x}<br>Sample: %{y}<br>Z-score: %{z:.2f}<extra></extra>"
  ) |> plotly::layout(
    title = "Corrected Data Heatmap (Top 30 by Variance, Z-scored)",
    xaxis = list(title = "", tickangle = 45, tickfont = list(size = 8)),
    yaxis = list(title = "", tickfont = list(size = 7)),
    margin = list(b = 120, l = 150)
  )
} else {
  cat("No metabolite columns found for heatmap.")
}
```

---

<p style="text-align:center; color:#94a3b8; font-size:0.85em;">
Generated by <strong>MStargetR::batchCorrectR</strong> on `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`
</p>
