---
title: "MStargetR Generic Workflow"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(MStargetR)
```

# User Parameters

Edit these variables before running.

```{r user-parameters}
# Required parameters
user_name    <- "NAME"                        # Your identifier
project_path <- "USER/PATH/TO/PROJECT"        # Path to project folder
qc_label     <- "QC"                          # QC sample tag (e.g., "LTR", "PQC", "VLTR")

# Sample classification tags (must include your qc_label)
sample_tags  <- c("sample", "control", "blank", "qc")

# Missing value threshold (% per metabolite)
mv_threshold <- 50

# Limit of detection (peak area). Values below this count as below-LOD.
# Instrument-/lab-specific -- set to your instrument's detection floor.
lod_threshold <- 5000

# MRM template for PeakForgeR (named list of .tsv/.csv paths, one per version)
mrm_template_peakforger <- list(
  v1 = "path/to/mrm_guide_v1.tsv"
  # Add more versions if needed:
  # v2 = "path/to/mrm_guide_v2.tsv"
)

# MRM template list for qcCheckR (named list of SIL + concentration guides per version)
mrm_template_qccheckr <- list(
  v1 = list(
    SIL_guide  = "path/to/mrm_guide_v1.tsv",
    conc_guide = "path/to/SIL_concentration_guide_v1.tsv"
  )
  # Add more versions if needed:
  # v2 = list(SIL_guide = "...", conc_guide = "...")
)

# Batch correction parameters (used inside qcCheckR)
batch_method  <- "QCRFSC"   # Options: "QCRFSC", "ComBat", "QCRLSC"
batch_ntree   <- 500         # Number of trees (QCRFSC only)
batch_coCV    <- 100         # CoCV threshold (%, 1-100)
batch_Frule   <- 0           # Filtering rule (0 = no filter)
batch_imputeM <- "minHalf"   # Imputation: "minHalf", "median", "mean", or "knn"
```

# Optional: Validate Templates

Run these checks before the pipeline to catch template errors early.

```{r validate-templates}
# Check for duplicate Q1/Q3 transitions
mrm_df <- read.delim(mrm_template_peakforger[["v1"]], check.names = FALSE)
transition_checkR(mrm_df)

# Check that MRM template and concentration guide entries match
conc_df <- read.delim(
  mrm_template_qccheckr[["v1"]]$conc_guide,
  check.names = FALSE
)
compare_mrm_template_with_guide(mrm_df, conc_df)
```

# Step 1: msConvertR -- Vendor File Conversion

Converts raw vendor files (WIFF, RAW, etc.) to mzML format via Docker.

```{r step1-msconvertr}
message("Step 1: Converting raw vendor files to mzML...")
msConvertR(
  input_directory  = project_path,
  output_directory = project_path
)
```

# Step 2: PeakForgeR -- Peak Picking and Integration

Processes mzML files using Skyline (via Docker) for peak picking, retention
time optimisation, and chromatographic integration.

```{r step2-peakforger}
message("Step 2: Running PeakForgeR...")
PeakForgeR(
  user_name         = user_name,
  project_directory = project_path,
  mrm_template_list = mrm_template_peakforger,
  QC_sample_label   = qc_label,
  plateID_outputs   = NULL    # NULL = process all plates
)
```

# Step 3: qcCheckR -- Quality Control and Reporting

Imports PeakForgeR reports, applies QC filtering, missing value imputation,
batch correction, PCA, and generates HTML/Excel reports.

```{r step3-qccheckr}
message("Step 3: Running QC check...")
qcCheckR(
  user_name         = user_name,
  project_directory = project_path,
  mrm_template_list = mrm_template_qccheckr,
  QC_sample_label   = qc_label,
  sample_tags       = sample_tags,
  mv_threshold      = mv_threshold,
  lod_threshold     = lod_threshold,
  batch_method      = batch_method,
  batch_ntree       = batch_ntree,
  batch_coCV        = batch_coCV,
  batch_Frule       = batch_Frule,
  batch_imputeM     = batch_imputeM
)
```

# Optional: Standalone Batch Correction

Use `batchCorrectR()` independently on any dataset with `sample_name`,
`batch`, `sample_type`, `run_order`, and numeric metabolite columns.

```{r optional-batchcorrectr}
# result <- batchCorrectR(
#   data       = my_data,       # data.frame or list of plate data.frames
#   qc_label   = "qc",
#   method     = "QCRFSC",      # "QCRFSC", "ComBat", or "QCRLSC"
#   ntree      = 500,
#   coCV       = 100,
#   Frule      = 0,
#   imputeM        = "minHalf",
#   output_dir     = file.path(project_path, "batch_correction"),
#   advanced_plots = TRUE,       # full GUI plot set (replaces deprecated 'plot')
#   report         = TRUE
# )
#
# corrected <- result$corrected_data
# result$correction_summary
```

# Session Info

```{r session-info}
sessionInfo()
```
