---
title: "MStargetR CCSM Workflow"
author: "Harrison Szemray"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(MStargetR)
```

# Single Project Workflow

ANPC CCSM lipidomics pipeline using built-in MRM templates and sample tags.

## User Parameters

```{r single-user-params}
project_path <- "USER/PATH/TO/PROJECT"   # Path to project folder
qc_label     <- "LTR"                    # Options: LTR, PQC, VLTR, etc.
mv_threshold <- 50                        # Missing value threshold (%)
lod_threshold <- 5000                     # Limit of detection (peak area)

# Batch correction parameters
batch_method  <- "QCRFSC"   # Options: "QCRFSC", "ComBat", "QCRLSC"
batch_ntree   <- 500
batch_coCV    <- 100
batch_Frule   <- 0
batch_imputeM <- "minHalf"
```

## Run Pipeline

```{r single-pipeline}
message("Step 1: Converting raw vendor files to mzML...")
msConvertR(
  input_directory  = project_path,
  output_directory = project_path
)

message("Step 2: Running PeakForgeR...")
PeakForgeR(
  user_name         = "ANPC",
  project_directory = project_path,
  mrm_template_list = NULL,           # Uses built-in ANPC templates
  QC_sample_label   = qc_label,
  plateID_outputs   = NULL
)

message("Step 3: Running QC check...")
qcCheckR(
  user_name         = "ANPC",
  project_directory = project_path,
  mrm_template_list = NULL,           # Uses built-in ANPC templates
  QC_sample_label   = qc_label,
  sample_tags       = NULL,           # Uses ANPC default tags
  mv_threshold      = mv_threshold,
  lod_threshold     = lod_threshold,
  batch_method      = batch_method,
  batch_ntree       = batch_ntree,
  batch_coCV        = batch_coCV,
  batch_Frule       = batch_Frule,
  batch_imputeM     = batch_imputeM
)

sessionInfo()
```

---

# Multi-Project Batch Workflow

Process multiple projects sequentially with per-project configuration.

## Project Configurations

```{r multi-configs}
project_configs <- list(
  list(
    path          = "USER/PATH/TO/PROJECT1",
    qc_label      = "PQC",
    mv_threshold  = 50,
    lod_threshold = 5000,
    batch_method  = "QCRFSC"
  ),
  list(
    path          = "USER/PATH/TO/PROJECT2",
    qc_label      = "LTR",
    mv_threshold  = 40,
    lod_threshold = 5000,
    batch_method  = "QCRFSC"
  ),
  list(
    path          = "USER/PATH/TO/PROJECT3",
    qc_label      = "VLTR",
    mv_threshold  = 60,
    lod_threshold = 5000,
    batch_method  = "QCRFSC"
  )
)
```

## Run All Projects

```{r multi-pipeline}
for (config in project_configs) {
  message("\n========================================")
  message("Processing: ", config$path)
  message("========================================\n")

  message("Step 1: Converting raw vendor files to mzML...")
  msConvertR(
    input_directory  = config$path,
    output_directory = config$path
  )

  message("Step 2: Running PeakForgeR...")
  PeakForgeR(
    user_name         = "ANPC",
    project_directory = config$path,
    mrm_template_list = NULL,
    QC_sample_label   = config$qc_label,
    plateID_outputs   = NULL
  )

  message("Step 3: Running QC check...")
  qcCheckR(
    user_name         = "ANPC",
    project_directory = config$path,
    mrm_template_list = NULL,
    QC_sample_label   = config$qc_label,
    sample_tags       = NULL,
    mv_threshold      = config$mv_threshold,
    lod_threshold     = config$lod_threshold,
    batch_method      = config$batch_method
  )
}

sessionInfo()
```

---

# Optional: Standalone Batch Correction

Use `batchCorrectR()` on any dataset independently of the main pipeline.

```{r standalone-batchcorrectr}
# result <- batchCorrectR(
#   data       = my_data,       # data.frame or list of plate data.frames
#   qc_label   = "ltr",
#   method     = "QCRFSC",
#   ntree      = 500,
#   coCV       = 100,
#   Frule      = 0,
#   imputeM        = "minHalf",
#   output_dir     = tempdir(),
#   advanced_plots = TRUE,       # full GUI plot set (replaces deprecated 'plot')
#   report         = TRUE
# )
#
# corrected <- result$corrected_data
# result$correction_summary
```

# Optional: ComBat Batch Correction

ComBat does not require QC samples and uses empirical Bayes methods.

```{r combat-example}
# result <- batchCorrectR(
#   data             = my_data,
#   method           = "ComBat",
#   combat_par.prior = TRUE,
#   combat_mean.only = FALSE,
#   combat_ref.batch = NULL,   # Reference batch (optional)
#   advanced_plots   = TRUE,   # full GUI plot set (replaces deprecated 'plot')
#   report           = TRUE
# )
```
